### 2016-04-30 ch01-intro/introduction.tex
CH01:

System identification is the scientific approach of converting observations of a system into mathematical models that describe the behavior of the system under test.
In \figref{fig:intro:identification-cycle}, a high-level flow diagram containing some key steps that are performed when identifying a system.
Note that this is a simplified view, different authors

@@

\paragraph{Can we }

>>>>

System identification is the science---and often art---to deals with converting observations of a system into mathematical models to describe the behavior of the system under test.
In \figref{fig:intro:identification-cycle}, a high-level flow diagram containing some key steps that are performed when identifying a system.
Note that this is a simplified view, different authors

@@

\paragraph{Can we avoid local minima by using smoothers?}
